### 2016-03-14 paper/conclusion.tex
spell checking

\section{Conclusion and future directions}
We have proposed a novel MRF inference framework, Swarm Fusion, in
parallel computing environments. The framework is general and makes
popular inference techniques such as Alpha Expansion, Fusion Move,
Parallel Alpha Expansion, and Hierarchical Fusion, its special cases. Our
experiments have revealed that the framework exploits parallel
computational resources and achieves faster convergence, epseically for
challenging problems.  Our first future work is to conduct experiments
on cloud computing environments, in particular, the MapReduce
programming model, where the roles of mappers and reducers exactly
correspond to the processes of parallel multi-way fusion and solution
sharing, respectively.  Another future work is the automatic
configuration of the Swarm Fusion architecture.  Our experiments have
shown that optimal architectures are different for different problems.
An interesting direction is to adaptively change its architecture during
the computation, for example, switching to simple parallel
alpha-expansion for easy problems, or increasing the rate of solution
exchanges when solutions vary significantly across threads.
%
Parallel MRF inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
framework require minimal coding. We believe that this paper would
immediately benefit tens of thousands of Computer Vision researchers or
engineers in the world, who currently solve MRF problems. We will share
our source code with the community.

>>>>

\section{Conclusion and future directions}
We have proposed a novel MRF inference framework, Swarm Fusion, in
parallel computing environments. The framework is general and makes
popular inference techniques such as Alpha Expansion, Fusion Move,
Parallel Alpha Expansion, and Hierarchical Fusion, its special cases. Our
experiments have revealed that the framework exploits parallel
computational resources and achieves faster convergence, especially for
challenging problems.  Our first future work is to conduct experiments
on cloud computing environments, in particular, the MapReduce
programming model, where the roles of mappers and reducers exactly
correspond to the processes of parallel multi-way fusion and solution
sharing, respectively.  Another future work is the automatic
configuration of the Swarm Fusion architecture.  Our experiments have
shown that optimal architectures are different for different problems.
An interesting direction is to adaptively change its architecture during
the computation, for example, switching to simple parallel
alpha-expansion for easy problems, or increasing the rate of solution
exchanges when solutions vary significantly across threads.
%
Parallel MRF inference has been a relatively under-explored topic in
Computer Vision. Our idea is very simple, where adapting the Swarm Fusion
framework require minimal coding. We believe that this paper would
immediately benefit tens of thousands of Computer Vision researchers or
engineers in the world, who currently solve MRF problems. We will share
our source code with the community.

### 2016-03-14 paper/result_layered_depthmap.tex
Hang
figure placement
spell checking

@@

At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N}).~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}  It is natural that our SF model find lower energy faster with more threads. While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not propotional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/layered_depthmap_convergence.png}
  \caption{Energy plots for the layered depthmap estimation
 problem. Both the multi-way fusion and the solution sharing are important
 for this challenging problem.}\label{fig:layered_depthmap_convergence}
\end{figure}

\begin{figure}[tb]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
    \caption{}
    \label{fig:optical_flow_by_alpha}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
    \caption{}
    \label{fig:optical_flow_by_N}
  \end{subfigure}
  \caption{(a) Energy plots for layered depthmap estimation with varying
    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
  \label{fig:layered_depthmap_by_alpha_N}
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/layered_depthmap_convergence.png}
  \caption{Energy plots for the layered depthmap estimation
    problem. Both the multi-way fusion and the solution sharing are important
    for this challenging problem.}\label{fig:layered_depthmap_convergence}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
    \caption{}
    \label{fig:layered_depthmap_by_alpha}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
    \caption{}
    \label{fig:layered_depthmap_by_N}
  \end{subfigure}
  \caption{(a) Energy plots for layered depthmap estimation with varying
    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
  \label{fig:layered_depthmap_by_alpha_N}
\end{figure}

@@

At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N}).~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}  It is natural that our SF model find lower energy faster with more threads. While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not proportional to the number of threads.
%We can see that as the number of
%ways to fuse becomes larger, each fusion step takes longer time, but the
%chance of finding a lower energy state increases.

### 2016-03-14 paper/result_optical_flow.tex
Hang
spell checking

\noindent
%
We have chosen the Dimetrodon image pair from the Middlebury flow
dataset~\cite{middlebury_optical_flow}. Figure~\ref{fig:optical_flow_convergence}
shows the energy plots of the three competing methods, Fusion Move
(FM), Parallel Fusion Move (PFM), and Hierarchical Fusion Move (HFM),
against our Swarm Fusion methods (SF-MF, SF-SS, SF). A key observation
is that SF-MF converges quicker and better than PFM. This is indeed the
benefits of solution sharing in our network. Optical flow is a more
difficult problem and many solution proposals are not effective.
The solution sharing (i.e., SF-MF) allows all the threads to exchange
effective solution proposals in the middle of the
optimization.
\begin{figure}[tb]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
    \caption{}
    \label{fig:optical_flow_PFM_threads}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
    \caption{}
    \label{fig:optical_flow_SF_MF_threads}
  \end{subfigure}
  \caption{Energy plots per thread for (a) Parallel Fusion  
    Move (PFM) and (b) our FS-MF.}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we did two more experiments. First, we set
$\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
revealed that the solution sharing makes convergence faster regarless of
$\beta$.  However, too much solution sharing slows down the converence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because we have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.
\begin{figure}[tb]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
    \caption{}
    \label{fig:optical_flow_by_beta}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
    \caption{}
    \label{fig:optical_flow_by_interval}
  \end{subfigure}
  \caption{Energy plots for optical flow with (a) varying
    $\beta$ and (b) varying solution sharing
    frequencies. Solution sharing achieves better convergence, but sharing too many solutions (larger $\beta$) or sharing solutions too frequently (less $k$) slows down the convergence, as it reduces the time for exploration.}
\end{figure}

>>>>

\noindent
%
We have chosen the Dimetrodon image pair from the Middlebury flow
dataset~\cite{middlebury_optical_flow}. Figure~\ref{fig:optical_flow_convergence}
shows the energy plots of the three competing methods, Fusion Move
(FM), Parallel Fusion Move (PFM), and Hierarchical Fusion Move (HFM),
against our Swarm Fusion methods (SF-MF, SF-SS, SF). A key observation
is that SF-MF converges quicker and better than PFM. This is indeed the
benefits of solution sharing in our network. Optical flow is a more
difficult problem and many solution proposals are not effective.
The solution sharing (i.e., SF-MF) allows all the threads to exchange
effective solution proposals in the middle of the
optimization.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
    \caption{}
    \label{fig:optical_flow_PFM_threads}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
    \caption{}
    \label{fig:optical_flow_SF_MF_threads}
  \end{subfigure}
  \caption{Energy plots per thread for (a) Parallel Fusion  
    Move (PFM) and (b) our FS-MF.}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we did two more experiments. First, we set
$\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
revealed that the solution sharing makes convergence faster regardless of
$\beta$.  However, too much solution sharing slows down the convergence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because we have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
    \caption{}
    \label{fig:optical_flow_by_beta}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
    \caption{}
    \label{fig:optical_flow_by_interval}
  \end{subfigure}
  \caption{Energy plots for optical flow with (a) varying
    $\beta$ and (b) varying solution sharing
    frequencies. Solution sharing achieves better convergence, but sharing too many solutions (larger $\beta$) or sharing solutions too frequently (less $k$) slows down the convergence, as it reduces the time for exploration.}
\end{figure}
